Clouds and Radiation in a mock-Walker Circulation

### 2020-04-24 Silvers_WalkerCell.tex
substantial chagnes to text, structure, and figures of Silvers_WalkerCell.tex

			% Activate to display a given date or no date
%\title{Using the Walker Circulation to connect low-level cloud changes to deep convective entrainment}
\title{Clouds and Radiation in a mock-Walker Circulation}
\authors{Levi G. Silvers, and Thomas Robinson}

@@

%\textbf{Key Points: choose three}
\begin{keypoints}
%  \item{At 25 km, simulations with parameterized shallow- and deep-convection exhibit asymmetries in the circulation, 
 % precipitation, and humidity fields resulting in a steady-state overturning circulation that is not centered on the SST
%  maximum.}
  \item{High and low clouds interact differently with longwave radiation to increase or decrease the mean precipitation, depending on which cloud type is dominant}
  \item{Interactions between clouds and radiation combined with parameterized convection act to shift the precipitation 
  maximum away from the SST maximum.}
  \item{The longwave cloud-radiative effect is a fundamental factor in establishing these asymmetries and leads to dramatic
  changes in the low-level clouds and boundary layer structure.}
  \item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
  region that is 40\% higher than for the coarser cases with parameterized convection.}
  \item{The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.}
\end{keypoints}

@@

% What are climate modelers doing to reduce uncertainties about cloud processes?
%The representation of clouds in climate models is the most stubborn contributor to uncertainty of the climate response to increased 
%greenhouse gases.  A few of the reasons clouds are difficult to represent in models are imprecise definitions of clouds, an existential 
%dependence on trace amounts of condensed water, the importance of microphysical processes at scales less than the grid-scale, 
%and the close coupling between atmospheric radiative fluxes, clouds, and the large-scale dynamical circulations of Earth.  
%To elucidate this coupling between clouds, radiation, and the large-scale circulations of the Earth, we simulate an 
%idealized equatorial tropical Pacific.

In the western Pacific warm sea surface temperatures prevail beneath rising atmospheric motion and deep convective 
storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low-level, 
non-precipitating clouds with a dry subsiding atmosphere above the stratus clouds.  These regions are 
connected by a large-scale circulation.  
We analyze an idealization of this circulation with high-resolution 
and coarse resolution simulations. 
%% and infer how deep convective heating in the west Pacific can influence the atmospheric cooling 
%%thousands of kilometers away in the east Pacific.  This cooling is a key ingredient in the determination of the 
%%Earth's sensitivity to 
%%changes in greenhouse gas concentrations.
%
%A high resolution (1km) cloud resolving model is used here as a benchmark to compare with the same model at lower 
%resolution (25km, 100km) configured 
%as a fully parameterized general circulation model.  Both models use approximately the same spatial domain.  The climate model used is 
%derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory.  By 
%dramatically decreasing the grid-spacing from its default configuration we resolve much more of the dynamical motion and eliminate 
%some of the statistical approximations of clouds, and thus more explicitly simulate some of their impacts.

@@

@@

%Without question, clouds are more than passive conglomerates of tracers in a turbulent fluid.  If an advance in our understanding of the role clouds play in our climate is desired, it is essential that we 
%learn to model the two way interaction between clouds and the circulation.  The radiative influence of clouds is one of the primary mechanisms by which they influence the circulation (imp of lwcre off).  
%Our scientific motivation for this study is to illuminate/clarify the ways in which the large-scale circulation connects regions of deep convective activity with the prevalent tropical shallow 
%convection and the radiatively critical stratocumulus cloud decks.  While the meridional temperature gradient is a fundamental driver of the large-scale circulation, and the Coriolis force is 
%critical in determining the characteristics of tropical waves and the tropical extra-tropical connections, we propose that all of the physics of importance to our particular questions are present 
%in the equatorial manifestation of the Walker circulation (perhaps better in conclusion).  

@@

%Current computing capabilities cannot come close to resolving all of the spatial scales which are important in the lifetime of clouds.  
%As a result, coarse resolution climate models must use statistical representations of the influences from unresolved clouds. 
%Ideally the statistics of the coarse model should represent the explicitly resolved clouds of the higher resolution model and in particular as resolution is increased and the statistical approximations eliminated, the solution of the coarse model should be informed by the solution of the high resolution model.  This approach will help to demonstrate that the influence of clouds on climate is not an intractable problem.

@@

%The paradigm of the Walker circulation includes many distinct manifestations of moist convection, interactions between radiation and clouds, as well as dynamical motions which range from
%sub-kilometer scales to roughly 10,000 km.     In addition to the scientific interest of the Walker circulation as a link between deep convection, shallow-convection, and stratocumulus clouds, the tropical 
%Pacific provides an ideal physical context with which to explore the sensitivities and strengths of theoretical models, high-resolution models and general circulation models.  
%The tropical system in the Pacific Ocean including deep, shallow, and mid-level convection, as well as stratocumulus cloud decks and sea-surface temperature gradients 
%represents a fascinating and useful microcosm of the ways in which clouds can interact with dynamic circulations.
%This region of the Earth system contains clues to the difficult questions of how clouds couple to the circulation and how the nonlinear interactions within the system contribute 
%to the cloud feedbacks to perturbations and the overall sensitivity of the system to anthropogenic forcing.
%Several studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, Kuang, 2012) have examined a 
%mock Walker circulation in the context of cloud resolving 
%simulations, or idealized theoretical models.   The comparison between CRMs and simple theory revealed several important 
%similarities (like what? See Bretherton et al., 2006) and a multiplicity of differing results (like what) for different CRM studies. 
%It thus remains unclear what GCM like models should be expected to produce in similar configurations.  
%The unique contribution from this study is to take a new CMIP6 atmospheric global climate model and to use it in the context of a
%simple mock-Walker circulation configuration while changing as little as possible from the parent model.  The model we 
%use (GFDL's AM4.0) is flexible enough to operate at grid-spacings ranging from 100km down to 1km in a doubly periodic 
%domain that is configured similar to the equatorial Pacific.  This allows us to use a single code base to compare a model 
%run at GCM-like resolution with a full suite of subgrid-scale paremeterizations with a cloud-resolving version of the same 
%model in which all convective activity is strictly explicit and many more of the important dynamic motions are resolved. 
%"Effects of cloud on atmospheric radiative cooling must be considered to get a realistic Walker circulation over specified SST. (just before equation 8 of Bretherton et al. 2006)."

%The atmosphere of Earth constantly radiates energy to space.  This cooling of the atmosphere is mostly balanced by warming from the release of latent energy by convective clouds and precipitation.  The details of this balance between cooling and warming determine the role that clouds play in setting the Earth's climate sensitivity.  However, clouds contribute to both warming and cooling of the atmosphere.  Deep convective storms and high clouds warm the atmosphere by trapping outgoing radiation and absorbing shortwave radiation while clouds at lower levels cool the atmosphere by reflecting the incoming radiation from the sun.  Previous research has repeatedly shown that low-level clouds are the single largest factor in the current uncertainty of the Earth's climate response to a doubling of $\rm{CO}_2$ concentration (Bony and Dufresne, 2005, Sherwood et al. 2014).  However, it has also been shown that the turbulent mixing of the atmosphere by deep convective clouds provides a strong control within climate models on the climate sensitivity (Zhao, 2014).  The goal of this project is to elucidate/explore the connection between these two pieces of evidence.
%Previous studies such as Held et al., 1993; Tompkins et la. 1998, Bretherton et al., 2005; Muller and Held, 2012; Wing and Emanual, 2014 have shown that idealized models are quite 
%sensitive to the details of the configuration such as domain size and resolution.  This lack of convergence among high resolution models makes it difficult to know what to expect from 
%lower resolution models with convective parameterizations which are relevant to our understanding of GCMs.  Part of the purpose of this paper is to use one modeling framework to
%illustrate just what is obtained from a coarse GCM-like model run with idealized boundary conditions.  We then use this modeling framework to compare the results obtained from simulations
%with a resolution of 100, 25, 2, and 1km.
%The goal of designing idealized numerical experiments is to develop a tool that is easier to understand than the system the idealization 
%is based on.  The goal of adding complexity to a climate model is to achieve a more `realistic' simulation, as compared to the observed 
%world.  These simulations are somewhere in the middle of those extremes.  We have decided to keep many of the complex elements of 
%the global climate model  so that we can hopefully better understand the parent model (AM4.0) while learning something concrete about 
%the observable world.  By retaining such complexities as interactive radiation, convective parameterization, and the Tiedtke large-scale 
%cloud scheme we run the risk creating an idealized model which is no easier to understand than the original parent

@@

%a simple design that incorporates additional complexity which is critical for the connection to observed atmospheric phenomena.

@@

%Our simulations are based on the equatorial tropical Pacific.   In the western Pacific warm sea surface temperatures exist beneath rising atmospheric motion and deep convective storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low level, non-precipitation clouds with a very dry atmosphere above the clouds.  These regions are connected by a large-scale circulation of winds.  By comparing this scenario in a high-resolution and coarse resolution simulation we can infer how deep convective heating in the west Pacific can influence the atmospheric cooling thousands of kilometers away in the east Pacific.

@@

%\textbf{Paragraphs of Introduction}
%\begin{itemize}
%\item{Within the tropical Pacific are strong overturning circulations, deep convective towers, abundant shallow cumulus, 
%  and cumulus congestus clouds.  The Hadley circulation connects the tropical pacific with subtropics and has been 
%  extensively studies (review paper?).  The circulation first 
%  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated 
%  by deep convection to the eastern Pacific region which tends to be populated more by shallow cumulus and, in the 
%  subtropics, stratocumulus clouds.  This circulation has come to be 
%  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; 
%  Bretherton et al., 2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on 
%  observations (Walker, Bjerknes), theory (Geisler, 1981), 
%  or modeling studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, Kuang, 2012)).  Some of these 
%  modeling studies have compared theoretical models with cloud
%  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker    
%  Circulation with simulations from a GCM used on a doubly periodic domain.    What about Johnson et al.?}
%  The reality is that we were also inspired by Schneider et al. 2017.  Is it possible to tie all that together in a sensible way?  
% Johnson et al. discusses the trade inversion and the high statitic stability in the subtropics.  He contrasts 
% the thermodynamic arguments of Kloesel and Albrecht (1989) 
%  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995.  What say I?
%\item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale
%  circulations.  Previous studies of RCE have proven to be a 
%  useful tool with which to explore the basic physics of climate and climate sensitivity, but they lack a large-scale circulation.  Many 
%  studies have also shown the importance and prevalence of convective self aggregation (CSA).  A mock-walker circulation with an
%  imposed SST gradient can be thought of as studying a partially constrained aggregating or organized system in a way that removes
%  some of the ambiguity.  The mock-Walker circulation also allows for a simple way of studying in physical space, the connection
%  between column relative humidity and circulation in a way that is directly tied to the physical state of the system rather than with
%  a forced compositing of the data  
%  \cite{Bretherton2005, Muller2012}.}
%\item{On the importance of reducing component, or sub-grid scale uncertainty through the use of both parameterized and explicit 
%  convection.  This paragraph could also cite papers which have helped to validate RCE in general, and the channel RCE configuration
%  in particular.  To what extent do RCE simulations of CSA agree between GCMs and CRMs?  Perhaps here I can hint at the utility of 
%  this methodology for unifying our understanding.}
%\end{itemize}

\textbf{Key Questions}
\begin{itemize}
  \item{How do clouds influence the Walker Circulation?}
  \item{To what extent are the deep convective clouds and the low-level clouds in the Walker Cell coupled?}
  \item{When simulating the Walker Circulation, how well does a GCM compare to a CRM?}  
\end{itemize}

Within the region of the tropical Pacific strong overturning circulations, deep convective towers, abundant shallow 
cumulus, and cumulus congestus clouds all interact with each other.  The Hadley circulation connects the tropical 
pacific with the subtropics and has been extensively studied (review paper?).  The circulation first 
  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is 
  dominated by deep 
  convection to the eastern Pacific region which tends to be populated more by shallow cumulus and, in the 
  subtropics, stratocumulus clouds.  This circulation has come to be 
  known as the Walker Circulation and while receiving less attention than the Hadley circulation, there have been 
  notable studies (e.g. Geisler, 1981; 
  \citeA{Raymond1994}; Bretherton et al., 
  2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on observations 
  (Walker, Bjerknes), theory 
  (Geisler, 1981), or modeling (\citeA{Grabowski2000}, Bretherton et al., 2006; Wofsy and Kuang, 2012, 
  Kuang, 2012)).  The modeling studies have primarily used models referred to as Cloud-system 
  Resolving Models (CRM), 
  which has meant a grid-spacing of less than 5km and no convective parameterization.    One of the primary 
  motivations of this paper is to compare cloud resolving model simulations 
  of the Walker Circulation with simulations from a GCM within a flexible dynamical framework that draws on a 
  single code base for both models.

  Overturning circulations in the tropical Pacific atmosphere encompass dynamical motions at a host of scales 
and the different cloud types interact with the circulation on scales ranging from meters to thousands of km's.  
The tropical Pacific is an ideal location to study interactions between clouds and the circulation 
because it combines strong overturning circulations, abundant shallow cumulus, congestus, and cumulonimbus 
clouds \cite{Johnson1999}, as well as stratocumulus cloud decks along the eastern extremities of the basin.
Can we hope to simulate all of this in a single idealized modeling context?   Our initial motivation for using the 
GFDL AM4 model on a doubly-periodic domain was to simulate a tropical Pacific-like region 
%that is rich in phenomena 
in the context of both a GCM and a CRM in the hopes that resolving more of the turbulent motions and circulations
would help us to better understand the physics and the mechanisms which are at work in the cloud-circulation
interactions of the tropical Pacific and improve our ability to model this region in a GCM.    The dynamical core 
of the current generation GFDL models is ideally suited to this task because it can easily be used over a wide 
range of resolutions and can solve either the hydrostatic or nonhydrostatic governing equations.

We perform a series of sensitivity experiments that highlight the different ways in which these experiments can equilibrate.  To 
show both the robust features of the simulations and the sensitive nature of the distribution of the precipitation maximum 
we test the impact of convective parameterization, longwave radiation interactions with clouds, domain size, 
and the resolution, or grid-spacing.  Elements of this study that distinguish it from previous research on the Walker 
circulation are the use of fully interactive radiation, and the direct comparisons with a state-of-the-art general circulation
model configuration.   Muller and Held, 2012 found that self-aggregation was sensitive to both domain 
size and resolution because of the sensitivity of the low-level clouds to these parameters.  % the longwave radiative cooling.

The paper is organized as follows.  Details of the model and the particular experiments used are described
in the next section.  The longwave cloud radiative effect is an important element for all of the experiments and will be 
discussed in all of the sections.   
Section three describes the tendency of experiments with parameterized convection to settle into states which 
do not mirror the symmetry of the prescribed sea surface temperature.   
Then, section four shows how the distribution of precipitation changes as a function of domain size.  
Section five will describe and contrast the Walker circulation in a GCM-like and a CRM-like configuration. 
Conclusions from this study will then be summarized.

>>>>

			% Activate to display a given date or no date
%\title{Using the Walker Circulation to connect low-level cloud changes to deep convective entrainment}
\title{Clouds and Radiation in a mock-Walker Circulation}
\authors{Levi G. Silvers\affil{1,*}, and Thomas Robinson\affil{2}}

\affiliation{1}{Princeton University/GFDL, Princeton, New Jersey, USA}
\affiliation{2}{SAIC, Science Applications International Corporation, Reston, VA, USA}
\affiliation{*}{Current Affiliation: School of Marine and Atmospheric Sciences, Stony Brook University, Stony Brook, NY, USA}

@@

%\textbf{Key Points: choose three}
\begin{keypoints}
%  \item{At 25 km, simulations with parameterized shallow- and deep-convection exhibit asymmetries in the circulation, 
 % precipitation, and humidity fields resulting in a steady-state overturning circulation that is not centered on the SST
%  maximum.}
  \item{High and low clouds interact differently with longwave radiation to increase or decrease the mean precipitation, depending on which cloud type is dominant}
  \item{Interactions between clouds and radiation combined with parameterized convection shift the precipitation 
  maximum away from the SST maximum.}
 % \item{The longwave cloud-radiative effect is a fundamental factor in establishing these asymmetries and leads to dramatic
 % changes in the low-level clouds and boundary layer structure.}
  \item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
  region that is 40\% higher than for the coarser cases with parameterized convection.}
%  \item{The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.}
\end{keypoints}

@@

% What are climate modelers doing to reduce uncertainties about cloud processes?
%The representation of clouds in climate models is the most stubborn contributor to uncertainty of the climate response to increased 
%greenhouse gases.  A few of the reasons clouds are difficult to represent in models are imprecise definitions of clouds, an existential 
%dependence on trace amounts of condensed water, the importance of microphysical processes at scales less than the grid-scale, 
%and the close coupling between atmospheric radiative fluxes, clouds, and the large-scale dynamical circulations of Earth.  
%To elucidate this coupling between clouds, radiation, and the large-scale circulations of the Earth, we simulate an 
%idealized equatorial tropical Pacific over a range of resolutions.

In the western Pacific warm sea surface temperatures (SST) prevail beneath rising atmospheric motion and deep convective 
storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low-level, 
non-precipitating clouds with a dry subsiding atmosphere above the stratus clouds.  These regions are 
connected by a large-scale circulation referred to as the Walker circulation.  
We analyze an idealization of this circulation to compare the multi-scale interactions between circulations,
cloud systems, and interactive radiation across experiments with grid-spacing ranging from 1km to 100km.  
These experiments thus span the range of resolutions between General Circulation Models (GCMs) and 
Cloud-system Resolving Models (CRMs).  
Our GCM-like experiments have a large low-level cloud fraction but the CRM-like experiments have more
upper-level clouds.  This difference in the dominant cloud type leads to opposite atmospheric responses 
to changes in the longwave cloud radiative effect (LWCRE).  An active LWCRE leads to increased 
precipitation for GCMs, but decreased precipitation for CRMs.  Decreasing the resolution to 1km and 2km
results in stronger overturning circulations, more condensate aloft, and less domain mean precipitation.

Numerous studies of the Walker Circulation have used simplified 
theoretical or numerical models.  The focus of this paper is to simulate a mock-Walker
Circulation with a full-physics General Circulation Model (GCM) run with idealized boundary conditions to provide 
a connection between the simpler models 
%and the complex interactions between clouds, 
%radiation and the large-scale circulation that are present in the tropical Pacific 
and current GCMs.
The climate model used is derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory (GFDL).  By dramatically decreasing the grid-spacing from its default configuration we resolve much more of the dynamical motion and eliminate 
some of the statistical approximations of clouds, and thus more explicitly simulate some of their impacts.
This work demonstrates that a mock-Walker circulation is a useful generalization of RCE that includes
a large-scale circulation.
%% and infer how deep convective heating in the west Pacific can influence the atmospheric cooling 
%%thousands of kilometers away in the east Pacific.  This cooling is a key ingredient in the determination of the 
%%Earth's sensitivity to changes in greenhouse gas concentrations (think radiator fins).
%
%Both models use approximately the same spatial domain.

@@

\section*{Plain Language Summary}
Interactions between clouds, radiation, and dynamics all contribute
to the large-scale tropical motions and are fundamental to the Walker circulation.  
The Walker circulation is the name of the loop consisting of westward surface winds towards the western tropical Pacific, 
strong upward motion and deep convection over that region, 
%of the western tropical Pacific, 
and the return eastward winds aloft that 
eventually sink towards the surface in the eastern Pacific basin.  
We focus on an idealization of the Walker circulation (a mock-Walker circulation) 
in which the strong rising motion and deep convection is driven by a patch of warm sea surface temperature (SST).  
%Interactions between the radiative flux of energy and clouds are fundamental to the nature of the Walker circulation.  
The results show that the response of the atmosphere to the 
radiative flux of energy depends strongly on the relative amount of clouds at different heights. % type of cloud that is dominant in the atmosphere.  
It is further shown that GCM-like models are dominated by low-clouds while CRM-like models 
are dominated by high-clouds.  This work also argues that an idealized Walker circulation is an 
excellent configuration with which to better understand the interactions between clouds, radiation and circulation 
and to push the development of models forward.   Models of mock-Walker circulations represents
an intermediate tier in a hierarchy of models between RCE and more Earth-like models.

%The clouds in this system play a fundamental role in setting the 
%characteristics of the mock-Walker circulation and the dominant cloud types are heavily dependent on 
%what type of model is used to simulate them.

%Our simulations are based on the equatorial tropical Pacific.   In the western Pacific warm sea surface temperatures exist beneath 
%rising atmospheric motion and deep convective storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface 
%temperatures and low-level, non-precipitation clouds with a very dry atmosphere above the clouds.  These regions are connected by a
 %large-scale circulation of winds.  By comparing this scenario in a high-resolution and coarse resolution simulation we can infer how deep 
 %convective heating in the west Pacific can influence the atmospheric cooling thousands of kilometers away in the east Pacific.

@@

%Clouds are much more than passive conglomerates of tracers in a turbulent fluid.  
%Without question, clouds are more than passive conglomerates of tracers in a turbulent fluid.  If an advance in our understanding 
%of the role clouds play in our climate is desired, it is essential that we learn to model the two-way interaction between clouds 
%and the circulation.  The radiative influence of clouds is one of the primary mechanisms by which they influence the circulation 
%(imp of lwcre off).  Our scientific motivation for this study is to illuminate/clarify the ways in which the large-scale circulation 
%connects regions of deep convective activity with the prevalent tropical shallow convection and the radiatively critical 
%stratocumulus cloud decks.  While the meridional temperature gradient is a fundamental driver of the large-scale circulation, and 
%the Coriolis force is critical in determining the characteristics of tropical waves and the tropical extra-tropical connections, we 
%propose that all of the physics of importance to our particular questions are present in the equatorial manifestation of the Walker 
%circulation.  
%
%Current computing capabilities cannot come close to resolving all of the spatial scales which are important in the lifetime of clouds.  
%As a result, coarse resolution climate models must use statistical representations of the influences from unresolved clouds. 
%Ideally the statistics of the coarse model should represent the explicitly resolved clouds of the higher resolution model and in 
%particular as resolution is increased and the statistical approximations eliminated, the solution of the coarse model should be 
%informed by the solution of the high resolution model.  Demonstration of this would help to show that the influence of clouds on 
%climate is not an intractable problem.
%
%The paradigm of the Walker circulation includes many distinct manifestations of moist convection, interactions between 
%radiation and clouds, as well as dynamical motions which range from sub-kilometer scales to roughly 10,000 km.     
%In addition to the scientific interest of the Walker circulation as a link between deep convection, shallow-convection, and 
%stratocumulus clouds, the tropical Pacific provides an ideal physical context with which to explore the sensitivities and 
%strengths of theoretical models, high-resolution models and general circulation models.  The tropical system in the Pacific 
%Ocean including deep, shallow, and mid-level convection, as well as stratocumulus cloud decks and sea-surface 
%temperature gradients represents a fascinating and useful microcosm of the ways in which clouds can interact with dynamic 
%circulations.  This region of the Earth system contains clues to the difficult questions of how clouds couple to the circulation 
%and how the nonlinear interactions within the system contribute to the cloud feedbacks to perturbations and the overall 
%sensitivity of the system to anthropogenic forcing.
%
%It remains unclear what GCM like models should be expected to produce in similar configurations.

%"Effects of cloud on atmospheric radiative cooling must be considered to get a realistic Walker circulation over specified 
%SST. (just before equation 8 of Bretherton et al. 2006)."

%The atmosphere of Earth constantly radiates energy to space.  This cooling of the atmosphere is mostly balanced by 
%warming from the release of latent energy by convective clouds and precipitation.  The details of this balance between 
%cooling and warming determine the role that clouds play in setting the Earth's climate sensitivity.  However, clouds 
%contribute to both warming and cooling of the atmosphere.  Deep convective storms and high clouds warm the 
%atmosphere by trapping outgoing radiation and absorbing shortwave radiation while clouds at lower levels cool the 
%atmosphere by reflecting the incoming radiation from the sun.  Previous research has repeatedly shown that low-level 
%clouds are the single largest factor in the current uncertainty of the Earth's climate response to a doubling of $\rm{CO}_2$ 
%concentration (Bony and Dufresne, 2005, Sherwood et al. 2014).  However, it has also been shown that the turbulent 
%mixing of the atmosphere by deep convective clouds provides a strong control within climate models on the climate 
%sensitivity (Zhao, 2014).  The goal of this project is to elucidate/explore the connection between these two pieces of evidence.

@@

%Previous studies such as Held et al., 1993; Tompkins et la. 1998, Bretherton et al., 2005; Muller and Held, 2012; Wing and 
%Emanual, 2014 have shown that idealized models are quite sensitive to the details of the configuration such as domain size 
%and resolution.  This lack of convergence among high resolution models makes it difficult to know what to expect from 
%lower resolution models with convective parameterizations which are relevant to our understanding of GCMs.  Part of the 
%purpose of this paper is to use one modeling framework to illustrate what is obtained from a coarse GCM-like model run 
%with idealized boundary conditions.  We then use this same modeling framework to compare the results obtained from 
%simulations with a resolution of 100, 25, 2, and 1km.     

@@

%The goal of designing idealized numerical experiments is to develop a tool that is easier to understand than the system 
%the idealization is based on.  The goal of adding complexity to a climate model is to achieve a more `realistic' simulation, 
%as compared to the observed world.  These simulations are somewhere in the middle of those extremes.  We have 
%decided to keep many of the complex elements of the global climate model  so that we can hopefully better understand 
%the parent model (AM4.0) while learning something concrete about 
%the observable world.  By retaining such complexities as interactive radiation, convective parameterization, and the Tiedtke 
%large-scale cloud scheme we run the risk creating an idealized model which is no easier to understand than the original parent

@@

%a simple design that incorporates additional complexity which strengthens the connection to observed atmospheric phenomena.

@@

@@

%  The reality is that we were also inspired by Schneider et al. 2017.  Is it possible to tie all that together in a sensible way?  
% Johnson et al. discusses the trade inversion and the high statitic stability in the subtropics.  He contrasts 
% the thermodynamic arguments of Kloesel and Albrecht (1989) 
%  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995.  What say I?
%\item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale
%  circulations.  Previous studies of RCE have proven to be a 
%  useful tool with which to explore the basic physics of climate and climate sensitivity, but they lack a large-scale circulation.  Many 
%  studies have also shown the importance and prevalence of convective self aggregation (CSA).  A mock-walker circulation with an
%  imposed SST gradient can be thought of as studying a partially constrained aggregating or organized system in a way that removes
%  some of the ambiguity.  The mock-Walker circulation also allows for a simple way of studying in physical space, the connection
%  between column relative humidity and circulation in a way that is directly tied to the physical state of the system rather than with
%  a forced compositing of the data  
%  \cite{Bretherton2005, Muller2012}.}

The tropical Pacific is an ideal location to study interactions between clouds and the circulation 
because it combines strong overturning circulations, abundant shallow cumulus, congestus, and cumulonimbus 
clouds \cite{Johnson1999} as well as stratocumulus cloud decks along the eastern extremities of the basin.
%Within the region of the tropical Pacific strong overturning circulations, deep convective towers, abundant shallow 
%cumulus, and cumulus congestus clouds all interact with each other.  
These overturning circulations encompass dynamical motions at scales
ranging from meters to thousands of km's all of which interact with each of the different cloud types.
% interact with the circulation on scales ranging from meters to thousands of km's.  
%The Hadley circulation connects the tropical pacific with the subtropics and has been extensively 
%studied (review paper?).  
The circulation first noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the 
Indonesian region that is dominated by deep convection to the eastern Pacific region which tends to 
be populated more by shallow cumulus and, in the subtropics, stratocumulus clouds.  
This circulation, now known as the Walker Circulation, is a response to the 
longitudinal asymmetries in the tropical atmospheric heating and is tightly coupled with 
the El Nino Southern Oscillation.    
The Walker Circulation is a compelling example of both thermodynamic and dynamic interactions
between moisture and the large-scale circulation.  It is also a framework that can be compared 
to observations and tested with a variety of model configurations.

% Part of our motivations in using the framework of the Walker circulation comes from the fact that 
% all of the major types of tropical clouds occur regularly within the region identified with the Walker
% circulation.  In addition, the ability to focus on the equator without rotational effects simplifies
% the dynamics.

It is also clear that the tropical Pacific plays an important role in the response of the climate to radiative perturbations. 
Recent work has shown that the interactions between clouds, patterns of Sea Surface Temperature (SST), and the circulation 
in the tropical Pacific play an important role in determining the cloud feedback and the decadal 
variability of the climate feedback 
\cite<e.g.,>[]{Andrews_Webb_2018, Zhou_etal_2016, Silvers_etal_2018, Fueglistaler_2019}.
While the Hadley circulation connects the tropics with the midlatitudes,  
the Walker circulation is one of the primary mechanisms by which the clouds, SST and circulations 
are coupled to each other in the tropics.  
%While the meridional temperature gradient is a fundamental driver of the large-scale circulation, and 
%the Coriolis force is critical in determining the characteristics of tropical waves and the tropical 
%extra-tropical connections, 
We propose that focusing on the Walker Circulation can lead to new insights into 
several questions that are critical to a better understanding of the tropical climate and cloud processes.    
These questions include: 
\begin{itemize}
  \item{How do clouds influence the overturning circulation?}
  \item{To what extent are the deep convective clouds and the low-level clouds coupled through 
  the overturning circulation?}
  \item{When simulating tropical overturning circulations, how well does a GCM compare to a CRM?}  
\end{itemize}
%These interactions are influenced not only by the Walker circulation, but also the Hadley 
%cell and convectively coupled tropical waves.  
In global and Earth-like GCM simulations, the interplay between the overturning 
circulation and clouds is difficult to disentangle from other active processes such as
the Hadley cell and convectively coupled tropical waves.  
%the large-scale circulation and clouds do not 
%act on each other in isolation but are also influenced by a host of other phenomena such as 
%the Hadley cell and convectively coupled tropical waves.  
Most of the studies with CRMs that have focused on the tropical overturning circulation in a more idealized 
context have been restricted to relatively small domain sizes and highly simplified physics parameterizations.  
The result is a gap in the types of simulation for this region that is so important to our 
understanding of clouds in the Earth's climate system.  
%The Walker circulation embodies an ideal combination of physical processes that can help us to connect the findings from CRMs, 
%GCMs, and the observed world.

% Deep convective towers release vast amounts of latent heat into the atmosphere and are part of the system
% that transports so much energy poleward.  Trade-wind cumulus and stratocumulus clouds influence the 
% Pacific-decadal oscillation and ENSO as well as reflecting vast amounts of insolation back to space.
% This region of the globe has been recognized to be of critical importance to the global energy budget 
% for decades (Rhiel and Malkus ?, Pierrehumbert, 1995?)

This work uses the framework of a mock-Walker circulation to simulate an overturning tropical circulation with 
both a GCM-like model and a CRM-like model.
 Idealized models of the Walker circulation were first called `mock-Walker circulations' by \citeA{Raymond_1994}.  
\citeA{Raymond_1994} envisioned an idealized Walker circulation as,``a possible venue for testing ideas 
about the interaction of dynamics, moist convection, and sea-air transfers that is simple enough to 
be understandable, but rich enough to be interesting."
Using the mock-Walker circulation as a tool to help distill the processes in complex climate models into 
concrete understanding was also proposed by \citeA{Jeevanjee_etal_2017}.
There have been many notable studies of the Walker Circulation \cite<e.g.,>[]{Geisler_1981, Raymond_1994, Grabowski2000, Tompkins_2001, Bretherton_Sobel_2002, Bretherton_etal_2006, Wofsy_Kuang_2012, Schwendike_etal_2014}.  
Previous studies have focused on observations \cite{Bjerknes1969, Schwendike_etal_2014}, theory \cite{Gill_1980, Geisler_1981, Raymond_1994,Bretherton_Sobel_2002}, or a combination of modeling and simple theory 
\cite{Grabowski2000, Sobel_etal_2004, Peters_Bretherton_2005, Bretherton_etal_2006, Wofsy_Kuang_2012,Kuang_2012}.  
The modeling studies have primarily used models we refer to as Cloud-system 
Resolving Models (CRMs; grid-spacing of less than 5km, no convective parameterization).  
Multiple studies have presented elegant conceptual and theoretical models of the overturning tropical circulation 
\cite{Raymond_1994, Pierrehumbert_1995, Larson_etal_1999, Bretherton_Sobel_2002}.  
However, these simplified theoretical models of the circulation differ from each other in important details and 
have different parameter dependencies.  
Their simplicity helps to provide insight into those models, but is difficult to translate
to the tropical climates produced by GCMs.  
Most of these previous studies greatly simplify both the radiation and the representation of clouds.  
They point to the importance of the interactions between clouds, radiation and the large-scale circulation while 
avoiding much of the complexity of those processes.   
%The work presented in this paper uses the full-physics of the recently developed GCM AM4.0
%in a context usually reserved for CRMs as a means to create more overlap between these 
%model types and help us to better understand the tropical climate.

%Several elements distinguish this study from previous research on the Walker 
%circulation.  
Current climate models continue to be developed with an increasingly fine resolution and 
the domain size used with CRMs continues to grow.  As a result the line between these two types 
of models has become blurred and there is a need to systematically compare the clouds and their 
influence on the climate produced by each type of model (Schneider et al., 2017).
By simulating a mock-Walker Circulation in the context of both a GCM and a CRM we 
illustrate how inextricable the interactions between clouds and radiation are to the coupling 
of moisture with the large-scale circulation.     
The model used here is based on the GFDL AM4.0 GCM that participated in CMIP6, 
having a full suite of physics parameterizations.  
%This includes fully interactive radiation and for the GCM-like cases convective parameterization 
% for both deep and shallow convective clouds.  
Rather than a full global domain all of our experiments use a doubly-periodic domain.  
%We use fully interactive radiation 
%(\citeA{Raymond_1994}; Tompkins, 2001; \citeA{Kuang_2012}; \citeA{Wofsy_Kuang_2012} used either fixed or gray radiative cooling).    
The combination of a doubly periodic domain and a current generation climate model allow us to analyze the interactions of the 
circulation and clouds in simulations with grid-spacing that ranges from 1km to 100km.  
We thus study a full-physics GCM in an idealized context that is relevant to observed tropical systems, to theoretical
models of the tropical circulation, and to many of the recent studies of radiative convective equilibrium (RCE).   
%Our experiments with a grid-spacing of 1km have a higher resolution then the previous studies with CRMs.
